Parallel multi-objective optimization using co-evolutionary islands and search space overlapping

### 2016-12-05 hpmoon-eswa.tex
Final version sent to ESWA

\begin{abstract}
Multi-objective optimization methods have gained interest in the last
years because the performance they can achieve solving real-world
problems. 
Many of these problems usually require a high-dimensional
decision space, and multi-objective Evolutionary Algorithms have been
successfully used in the past. 
Due to the large computational cost
these algorithms require, different parallelization and distribution
methods have been proposed, with different parallel and distributed
computer architectures to cope with them. One of the most extended
methods are the distributed co-evolutionary algorithms, where each
processor deals only with a part of the decision space, that is, the
individuals belonging to the same sub-population (island) explore the
same subset of decision variables.
%After explaining the method, you should say why it might work - JJ

In this paper, a new method to automatically adapt the overlapping
sections of the individuals has been compared to other collaborative
% what sections? Decision space sections? Besides, you are using
% section here and before you were using "subset" - JJ
evolutionary methods. 
Different number of islands, chromosome sizes and problems have been
used. The analysis of the obtained experimental results, by using
different  
metrics, shows that coevolutionary approaches can provide
statistically significant improvements with respect to the base
algorithm, being the method to automatically adapt the overlapping
size the one to obtain the best performance during the same execution
time. Results also show that the relation of the number of  
islands (subpopulations) to the length of the chromosome (number of
decision variables) is also a relevant factor to determine the most
efficient alternative to distribute the decision variables.
\end{abstract}

@@

\bibliographystyle{elsarticle-num}

\bibliography{hpmoon-fgcs}
%\begin{thebibliography}{99}
%\bibitem[Kopka and Daly(2003)]{R1}
%Kopka~H and Daly~PW (2003) \textit{A Guide to \LaTeX}, 4th~edn.
%Addison-Wesley.%

%\bibitem[Lamport(1994)]{R2}
%Lamport~L (1994) \textit{\LaTeX: a Document Preparation System},
%2nd~edn. Addison-Wesley.%

%\bibitem[Mittelbach and Goossens(2004)]{R3}
%Mittelbach~F and Goossens~M (2004) \textit{The \LaTeX\ Companion},
%2nd~edn. Addison-Wesley.%

%\end{thebibliography}

>>>>

\begin{abstract}
Multi-objective optimization methods have gained interest in the last years because the performance they can achieve solving real-world problems. Many of these problems usually require a high-dimensional decision space, and multi-objective Evolutionary Algorithms have been successfully used in the past. Due to the large computational cost these algorithms require, different parallelization and distribution methods have been proposed, with different parallel and distributed computer architectures to cope with them. One of the most extended methods are the distributed co-evolutionary algorithms, where each processor deals only with a part of the decision space, that is, the individuals belonging to the same sub-population (island) explore the same subset of decision variables.

In this paper, a new method to automatically adapt the overlapping sections of the individuals has been compared to other collaborative evolutionary methods. Different number of islands, chromosome sizes and problems have been used. The analysis of the obtained experimental results, by using different metrics, shows that coevolutionary approaches can provide statistically significant improvements with respect to the base algorithm, being the method to automatically adapt the overlapping size the one to obtain the best performance during the same execution time. Results also show that the relation of the number of islands (subpopulations) to the length of the chromosome (number of decision variables) is also a relevant factor to determine the most efficient alternative to distribute the decision variables.
\end{abstract}

@@

%\bibliographystyle{elsarticle-num}

%\bibliography{hpmoon-eswa}

\begin{thebibliography}{10}
\expandafter\ifx\csname url\endcsname\relax
  \def\url#1{\texttt{#1}}\fi
\expandafter\ifx\csname urlprefix\endcsname\relax\def\urlprefix{URL }\fi
\expandafter\ifx\csname href\endcsname\relax
  \def\href#1#2{#2} \def\path#1{#1}\fi

\bibitem{Alba13parallel}
E.~Alba, G.~Luque, S.~Nesmachnow, Parallel metaheuristics: recent advances and
  new trends, International Transactions in Operational Research 20~(1) (2013)
  1--48.
\newblock \href {http://dx.doi.org/10.1111/j.1475-3995.2012.00862.x}
  {\path{doi:10.1111/j.1475-3995.2012.00862.x}}.

\bibitem{Folino03cellular}
G.~Folino, C.~Pizzuti, G.~Spezzano, A scalable cellular implementation of
  parallel genetic programming, {IEEE} Trans. Evolutionary Computation 7~(1)
  (2003) 37--53.

\bibitem{Alba02Parallelism}
E.~Alba, M.~Tomassini, Parallelism and evolutionary algorithms, {IEEE} Trans.
  Evolutionary Computation 6~(5) (2002) 443--462.

\bibitem{Luna15Survey}
F.~Luna, E.~Alba, Parallel multiobjective evolutionary algorithms, in:
  J.~Kacprzyk, W.~Pedrycz (Eds.), Springer Handbook of Computational
  Intelligence, Springer, 2015, pp. 1017--1031.

\bibitem{Branke04Parallelizingcone}
J.~Branke, H.~Schmeck, K.~Deb, R.~S. Maheshwar, Parallelizing multi-objective
  evolutionary algorithms: cone separation, in: Proceedings of the {IEEE}
  Congress on Evolutionary Computation, {CEC} 2004, 19-23 June 2004, Portland,
  OR, {USA}, {IEEE}, 2004, pp. 1952--1957.

\bibitem{Mukhopadhyay14Survey}
A.~Mukhopadhyay, U.~Maulik, S.~Bandyopadhyay, C.~A.~C. Coello, A survey of
  multiobjective evolutionary algorithms for data mining: Part {I}, {IEEE}
  Trans. Evolutionary Computation 18~(1) (2014) 4--19.

\bibitem{Chavez15MO}
F.~C. de~la O, E.~Clemente, D.~E. Hern{\'{a}}ndez, F.~F. de~Vega, G.~Olague, A
  multi-objective evolutionary algorithm for interaction systems based on laser
  pointers, in: A.~M. Mora, G.~Squillero (Eds.), Applications of Evolutionary
  Computation - 18th European Conference, EvoApplications 2015, Copenhagen,
  Denmark, April 8-10, 2015, Proceedings, Vol. 9028 of Lecture Notes in
  Computer Science, Springer, 2015, pp. 504--516.
\newblock \href {http://dx.doi.org/10.1007/978-3-319-16549-3}
  {\path{doi:10.1007/978-3-319-16549-3}}.

\bibitem{Hidalgo16residualstress}
J.~I. Hidalgo, R.~Fern{\'{a}}ndez, J.~M. Colmenar, F.~Cioffi, J.~L.
  Risco{-}Mart{\'{\i}}n, G.~Gonz{\'{a}}lez{-}Doncel, Using evolutionary
  algorithms to determine the residual stress profile across welds of
  age-hardenable aluminum alloys, Appl. Soft Comput. 40 (2016) 429--438.
\newblock \href {http://dx.doi.org/10.1016/j.asoc.2015.11.004}
  {\path{doi:10.1016/j.asoc.2015.11.004}}.

\bibitem{Gong15models}
Y.~Gong, W.~Chen, Z.~Zhan, J.~Zhang, Y.~Li, Q.~Zhang, J.~Li, Distributed
  evolutionary algorithms and their models: {A} survey of the state-of-the-art,
  Appl. Soft Comput. 34 (2015) 286--300.
\newblock \href {http://dx.doi.org/10.1016/j.asoc.2015.04.061}
  {\path{doi:10.1016/j.asoc.2015.04.061}}.

\bibitem{Tonda12cooperative}
A.~P. Tonda, E.~Lutton, G.~Squillero, A benchmark for cooperative coevolution,
  Memetic Computing 4~(4) (2012) 263--277.
\newblock \href {http://dx.doi.org/10.1007/s12293-012-0095-x}
  {\path{doi:10.1007/s12293-012-0095-x}}.

\bibitem{Kimovski15Parallel}
D.~Kimovski, J.~Ortega, A.~Ortiz, R.~Ba{\~{n}}os, Parallel alternatives for
  evolutionary multi-objective optimization in unsupervised feature selection,
  Expert Syst. Appl. 42~(9) (2015) 4239--4252.
\newblock \href {http://dx.doi.org/10.1016/j.eswa.2015.01.061}
  {\path{doi:10.1016/j.eswa.2015.01.061}}.

\bibitem{Dorronsoro13superlinear}
B.~Dorronsoro, G.~Danoy, A.~J. Nebro, P.~Bouvry, Achieving super-linear
  performance in parallel multi-objective evolutionary algorithms by means of
  cooperative coevolution, Computers {\&} {OR} 40~(6) (2013) 1552--1563.
\newblock \href {http://dx.doi.org/10.1016/j.cor.2011.11.014}
  {\path{doi:10.1016/j.cor.2011.11.014}}.

\bibitem{Garcia16hpmoon}
P.~Garc{\'{\i}}a{-}S{\'{a}}nchez, J.~Ortega, J.~Gonz{\'{a}}lez, P.~A. Castillo,
  J.~J. Merelo, Addressing high dimensional multi-objective optimization
  problems by coevolutionary islands with overlapping search spaces, in:
  G.~Squillero, P.~Burelli (Eds.), Applications of Evolutionary Computation -
  19th European Conference, EvoApplications 2016, Porto, Portugal, March 30 -
  April 1, 2016, Proceedings, Part {II}, Vol. 9598 of Lecture Notes in Computer
  Science, Springer, 2016, pp. 107--117.

\bibitem{Deb00NSGAII}
K.~Deb, S.~Agrawal, A.~Pratap, T.~Meyarivan, A fast elitist non-dominated
  sorting genetic algorithm for multi-objective optimisation: {NSGA-II}, in:
  M.~Schoenauer, K.~Deb, G.~Rudolph, X.~Yao, E.~Lutton, J.~J.~M. Guerv{\'{o}}s,
  H.~Schwefel (Eds.), Parallel Problem Solving from Nature - {PPSN} VI, 6th
  International Conference, Paris, France, September 18-20, 2000, Proceedings,
  Vol. 1917 of Lecture Notes in Computer Science, Springer, 2000, pp. 849--858.

\bibitem{DBLP:series/ncs/EibenS15}
A.~E. Eiben, J.~E. Smith, Introduction to Evolutionary Computing, Natural
  Computing Series, Springer, 2015.
\newblock \href {http://dx.doi.org/10.1007/978-3-662-44874-8}
  {\path{doi:10.1007/978-3-662-44874-8}}.

\bibitem{DeJong2006}
K.~A. De~Jong, Evolutionary computation: a unified approach, MIT press, 2006.

\bibitem{Mora13paretobased}
A.~M. Mora, P.~Garc{\'{\i}}a{-}S{\'{a}}nchez, J.~J.~M. Guerv{\'{o}}s, P.~A.
  Castillo, Pareto-based multi-colony multi-objective ant colony optimization
  algorithms: an island model proposal, Soft Comput. 17~(7) (2013) 1175--1207.
\newblock \href {http://dx.doi.org/10.1007/s00500-013-0993-y}
  {\path{doi:10.1007/s00500-013-0993-y}}.

\bibitem{Talbi08Parallel}
E.~Talbi, S.~Mostaghim, T.~Okabe, H.~Ishibuchi, G.~Rudolph, C.~A.~C. Coello,
  Parallel approaches for multiobjective optimization, in: J.~Branke, K.~Deb,
  K.~Miettinen, R.~Slowinski (Eds.), Multiobjective Optimization, Interactive
  and Evolutionary Approaches [outcome of Dagstuhl seminars]., Vol. 5252 of
  Lecture Notes in Computer Science, Springer, 2008, pp. 349--372.

\bibitem{Durillo08masterslave}
A.~J. Nebro, J.~J. Durillo, A study of the parallelization of the
  multi-objective metaheuristic {MOEA/D}, in: C.~Blum, R.~Battiti (Eds.),
  Learning and Intelligent Optimization, 4th International Conference, {LION}
  4, Venice, Italy, January 18-22, 2010. Selected Papers, Vol. 6073 of Lecture
  Notes in Computer Science, Springer, 2010, pp. 303--317.
\newblock \href {http://dx.doi.org/10.1007/978-3-642-13800-3}
  {\path{doi:10.1007/978-3-642-13800-3}}.

\bibitem{Hiroyasu07discussion}
T.~Hiroyasu, K.~Yoshii, M.~Miki, Discussion of parallel model of
  multi-objective genetic algorithms on heterogeneous computational resources,
  in: H.~Lipson (Ed.), Genetic and Evolutionary Computation Conference, {GECCO}
  2007, Proceedings, London, England, UK, July 7-11, 2007, {ACM}, 2007, p. 904.

\bibitem{Deb03distributed}
K.~Deb, P.~Zope, A.~Jain, Distributed computing of pareto-optimal solutions
  with evolutionary algorithms, in: C.~M. Fonseca, P.~J. Fleming, E.~Zitzler,
  K.~Deb, L.~Thiele (Eds.), Evolutionary Multi-Criterion Optimization, Second
  International Conference, {EMO} 2003, Faro, Portugal, April 8-11, 2003,
  Proceedings, Vol. 2632 of Lecture Notes in Computer Science, Springer, 2003,
  pp. 534--549.

\bibitem{Xiao03specialized}
N.~Xiao, M.~P. Armstrong, A specialized island model and its application in
  multiobjective optimization, in: E.~Cant{\'{u}}{-}Paz, J.~A. Foster, K.~Deb,
  L.~Davis, R.~Roy, U.~O'Reilly, H.~Beyer, R.~K. Standish, G.~Kendall, S.~W.
  Wilson, M.~Harman, J.~Wegener, D.~Dasgupta, M.~A. Potter, A.~C. Schultz,
  K.~A. Dowsland, N.~Jonoska, J.~F. Miller (Eds.), Genetic and Evolutionary
  Computation - {GECCO} 2003, Genetic and Evolutionary Computation Conference,
  Chicago, IL, USA, July 12-16, 2003. Proceedings, Part {II}, Vol. 2724 of
  Lecture Notes in Computer Science, Springer, 2003, pp. 1530--1540.

\bibitem{Wang09parallel}
W.~Zhi-xin, G.~Ju, A parallel genetic algorithm in multi-objective
  optimization, in: Control and Decision Conference, 2009. CCDC '09. Chinese,
  2009, pp. 3497--3501.
\newblock \href {http://dx.doi.org/10.1109/CCDC.2009.5192490}
  {\path{doi:10.1109/CCDC.2009.5192490}}.

\bibitem{Martens13asynchronous}
M.~M{\"{a}}rtens, D.~Izzo, The asynchronous island model and {NSGA-II:} study
  of a new migration operator and its performance, in: C.~Blum, E.~Alba (Eds.),
  Genetic and Evolutionary Computation Conference, {GECCO} '13, Amsterdam, The
  Netherlands, July 6-10, 2013, {ACM}, 2013, pp. 1173--1180.

\bibitem{cheng2015adaptive}
R.~Cheng, Y.~Jin, K.~Narukawa, Adaptive reference vector generation for inverse
  model based evolutionary multiobjective optimization with degenerate and
  disconnected pareto fronts, in: Evolutionary Multi-Criterion Optimization,
  Springer International Publishing, 2015, pp. 127--140.

\bibitem{zdt2000a}
E.~Zitzler, K.~Deb, L.~Thiele, {Comparison of Multiobjective Evolutionary
  Algorithms: Empirical Results}, Evolutionary Computation 8~(2) (2000)
  173--195.

\bibitem{ECJ}
S.~Luke, et~al., {ECJ: A Java-based Evolutionary Computation and Genetic
  Programming Research System}, available at
  \url{http://www.cs.umd.edu/projects/plus/ec/ecj} (2009).

\end{thebibliography}
